Differentiation By Year

### 2017-08-17 doc/RMD/by-year.Rmd
adjust supplementary plots

```{r NEplot, fig.width = 10, fig.height = 10}
gglNE <- suppressMessages(ggloc(loc, "NE", 2003:2012))
cowplot::plot_grid(plotlist = gglNE, labels = names(gglNE), ncol = 2)
```
```{r MIplot, fig.width = 10, fig.height = 10}
gglMI <- suppressMessages(ggloc(loc, "MI", 2003:2012))
cowplot::plot_grid(plotlist = gglMI, labels = names(gglMI), ncol = 2)
```

>>>>

```{r NEplot, fig.width = 10, fig.height = 12}
gglNE <- suppressMessages(ggloc(loc, "NE", 2003:2012))
cowplot::plot_grid(plotlist = gglNE, labels = names(gglNE), ncol = 2)
```
```{r MIplot, fig.width = 10, fig.height = 12}
gglMI <- suppressMessages(ggloc(loc, "MI", 2003:2012))
cowplot::plot_grid(plotlist = gglMI, labels = names(gglMI), ncol = 2)
```
